An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-21 indicators/paper/paper.tex

% Middle authors
\author[i]{Sumit Agrawal}
\author[l]{Wael Al Saeed}
\author[g]{Taylor Arnold}
\author[j]{Amartya Basu}
\author[d]{Jacob Bien}
\author[r]{{\'A}ngel A. Cabrera}
\author[b]{Andrew Chin}
\author[b]{Eu Jing Chua}
\author[b]{Brian Clark}
\author[i]{Sarah Colquhoun}
\author[b]{Nat DeFries}
\author[i]{David C. Farrow}
\author[r]{Jodi Forlizzi}
\author[i]{Jed Grabman}
\author[b]{Samuel Gratzl}
\author[a]{Alden Green}
\author[r]{Robin Han}
\author[i]{Kate Harwood}
\author[a,b]{Addison J. Hu}
\author[i]{Raphael Hyde}
\author[d]{Sangwon Hyun}
\author[l]{Ananya Joshi}
\author[h]{Jimi Kim}
\author[r]{Andrew Kuznetsov}
\author[b]{Wichada La Motte-Kerr}
\author[e,f]{Balasubramanian Narasimhan}
\author[r]{Yeon Jin Lee}
\author[p]{Kenneth Lee}
\author[b]{Zachary C. Lipton}
\author[r]{Michael X. Liu}
\author[k]{Lester Mackey}
\author[b]{Kathryn Mazaitis}
\author[o]{Daniel J. McDonald}
\author[i]{Phillip McGuinness}
\author[i]{Michael P. O'Brien}
\author[a,b]{Natalia L. Oliveira}
\author[a,b]{Pratik Patil}
\author[r]{Adam Perer}
\author[b]{Collin A. Politsch}
\author[l]{Dawn Rucker}
\author[i]{Chris Scott}
\author[s]{Nigam Shah}
\author[n]{Vishnu Shankar}
\author[p]{James Sharpnack}
\author[b]{Dmitry Shemetov}
\author[q]{Noah Simon}
\author[i]{Benjamin Y. Smith}
\author[b]{Vishakha Srivastava}
\author[e,f]{Robert Tibshirani}
\author[e]{Elena Tuzhilina}
\author[b]{Ana Karina Van Nortwick}
\author[a]{Val{\'e}rie Ventura}
\author[a]{Larry Wasserman}
\author[i]{Benjamin Weaver}
\author[m]{Jeremy C. Weiss}
\author[i]{Spencer Whitman}
\author[r]{Kristin Williams}

@@

\affil[a]{Department of Statistics \& Data Science, Carnegie Mellon University}
\affil[b]{Machine Learning Department, Carnegie Mellon University}
\affil[c]{Computational Biology Department, Carnegie Mellon University}
\affil[d]{Department of Data Sciences and Operations, University of Southern California}
\affil[e]{Department of Statistics, Stanford University}
\affil[f]{Department of Biomedical Data Science, Stanford University}
\affil[g]{Linguistics Program, University of Richmond}
\affil[h]{School of Natural Sciences and Mathematics, University of Texas at Dallas}
\affil[i]{Google.org}
\affil[j]{Information Networking Institute, Carnegie Mellon University}
\affil[k]{Microsoft Research New England}
\affil[l]{Computer Science Department, Carnegie Mellon University}
\affil[m]{Heinz College of Information Systems and Public Policy, Carnegie
  Mellon University}
\affil[n]{Program in Immunology, Stanford University School of Medicine}
\affil[o]{Department of Statistics, University of British Columbia}
\affil[p]{Department of Statistics, University of California, Davis}
\affil[q]{Department of Biostatistics, University of Washington}
\affil[r]{Human-Computer Interaction Institute, Carnegie Mellon University}
\affil[s]{Department of Medicine, Stanford University}

>>>>

% Middle authors
\author[d]{Sumit Agrawal} 
\author[e]{Wael Al Saeed} 
\author[f]{Taylor Arnold} 
\author[g]{Amartya Basu}
\author[h]{Jacob Bien} 
\author[i]{{\'A}ngel A. Cabrera} 
\author[b]{Andrew Chin}
\author[b]{Eu Jing Chua}
\author[b]{Brian Clark}
\author[d]{Sarah Colquhoun}
\author[b]{Nat DeFries}
\author[d]{David C. Farrow}
\author[i]{Jodi Forlizzi}
\author[d]{Jed Grabman}
\author[b]{Samuel Gratzl}
\author[a]{Alden Green}
\author[i]{Robin Han}
\author[d]{Kate Harwood}
\author[a,b]{Addison J. Hu}
\author[d]{Raphael Hyde}
\author[h]{Sangwon Hyun}
\author[e]{Ananya Joshi}
\author[j]{Jimi Kim}
\author[i]{Andrew Kuznetsov}
\author[b]{Wichada La Motte-Kerr}
\author[i]{Yeon Jin Lee}
\author[k]{Kenneth Lee} 
\author[b]{Zachary C. Lipton}
\author[i]{Michael X. Liu}
\author[l]{Lester Mackey} 
\author[b]{Kathryn Mazaitis}
\author[m]{Daniel J. McDonald} 
\author[d]{Phillip McGuinness}
\author[n,o]{Balasubramanian Narasimhan} 
\author[d]{Michael P. O'Brien}
\author[a,b]{Natalia L. Oliveira}
\author[a,b]{Pratik Patil}
\author[i]{Adam Perer}
\author[b]{Collin A. Politsch}
\author[o]{Samyak Rajanala}
\author[e]{Dawn Rucker}
\author[d]{Chris Scott}
\author[p]{Nigam Shah} %s
\author[q]{Vishnu Shankar} %n
\author[k]{James Sharpnack}
\author[b]{Dmitry Shemetov}
\author[r]{Noah Simon} %q
\author[d]{Benjamin Y. Smith}
\author[b]{Vishakha Srivastava}
\author[k]{Shiyu Tan}
\author[n,o]{Robert Tibshirani}
\author[n]{Elena Tuzhilina}
\author[b]{Ana Karina Van Nortwick}
\author[a]{Val{\'e}rie Ventura}
\author[a,b]{Larry Wasserman}
\author[d]{Benjamin Weaver}
\author[s]{Jeremy C. Weiss} %m
\author[d]{Spencer Whitman}
\author[i]{Kristin Williams}

@@

\affil[a]{Department of Statistics \& Data Science, Carnegie Mellon University}
\affil[b]{Machine Learning Department, Carnegie Mellon University}
\affil[c]{Computational Biology Department, Carnegie Mellon University}
\affil[d]{Google.org}
\affil[e]{Computer Science Department, Carnegie Mellon University}
\affil[f]{Linguistics Program, University of Richmond}
\affil[g]{Information Networking Institute, Carnegie Mellon University}
\affil[h]{Department of Data Sciences and Operations, University of Southern California}
\affil[i]{Human-Computer Interaction Institute, Carnegie Mellon University}
\affil[j]{School of Natural Sciences and Mathematics, University of Texas at Dallas}
\affil[k]{Department of Statistics, University of California, Davis}
\affil[l]{Microsoft Research New England}
\affil[m]{Department of Statistics, University of British Columbia}
\affil[n]{Department of Statistics, Stanford University}
\affil[o]{Department of Biomedical Data Science, Stanford University}
\affil[p]{Department of Medicine, Stanford University}
\affil[q]{Program in Immunology, Stanford University School of Medicine}
\affil[r]{Department of Biostatistics, University of Washington}
\affil[s]{Heinz College of Information Systems and Public Policy, Carnegie
  Mellon University}
